### 2017-01-26 main.tex
Minor edits related to the reviewer feedback

\begin{enumerate}
\item Record and align a corpus of training songs.  The technique has been published in \cite{Poole2012}. 200 songs generally yield acceptable results, but here we standardise on 1000-song training sets.
\item Choose one or more instants in the song that should create a trigger event, and train a
  neural network to recognise them. This step is carried out offline.  While any neural network software would produce similar results, we used MATLAB 2015b's neural network toolbox.
\item Once trained and saved, the neural network is used by a realtime
  detection programme that listens to an audio signal and indicates detection of the target
  syllables via a TTL pulse.  We present three implementations, in MATLAB, LabVIEW, and Swift, that trade off hardware requirements, ease of maintenance, and performance.
\end{enumerate}
This method makes the following contributions:
\begin{itemize}
\item Fast: sub-millisecond latencies, with jitter around 2 ms.
\item Accurate: false negative rates under 1\% and false positive rates under 0.001\% for a variety of syllables.
\item State-of-the-art performance with default parameters.
\item Requires almost no programming experience.
\item Runs on inexpensive hardware.
\item Described in detail here, with reference implementations provided and benchmarked.
\end{itemize}

@@

Because the data set consists of temporally aligned songs, the moment
at which detection should occur during each song sample is available
(albeit with minor variations due to the alignment process used
\cite{Poole2012}).  The detector can be checked by comparing its
response to the recorded training song samples against these
``canonical'' detection events.  To this end, besides the trained
network object, our learning code produces an audio file consisting of
all of the training data on the left audio channel and a delta
function at each aligned moment of target syllable presentation on the
right channel. Thus, when played on any audio player, the left channel
may be provided as input to the detector, and the the detector's
output pulses may be compared against the right channel.

@@

We define latency as the time between the training target (during our tests, this is indicated by the canonical
signal in the test file) and the corresponding detection event.  It is a helpful number,
but not a critical one, since in zebra finch a detector with high but
constant latency can often be trained to trigger at a point somewhat
before the true moment of interest (for example, if triggering should
occur at the very beginning of a syllable, the detector may be trained to recognise the previous syllable and the gap thereafter).  Usually the variability in latency is the more important number.  We define jitter as the standard deviation of detection latency over the test songs.

>>>>

\begin{enumerate}
\item Record and align a corpus of training songs.  The technique has been published in \cite{Poole2012}. 200 songs generally yield acceptable results, but here we standardise on 1000-song training sets.
\item Choose one or more instants in the song that should create a trigger event, and train a
  neural network to recognise them. This step is carried out offline.  While any neural network software would produce similar results, we used MATLAB 2015b's neural network toolbox.
\item Once trained and saved, the neural network is used by a realtime
  detection programme that listens to an audio signal and indicates detection of the target
  syllables via a TTL pulse.  We present three detection implementations, in MATLAB, LabVIEW, and Swift, that trade off hardware requirements, ease of maintenance, and performance.
\end{enumerate}
This method makes the following contributions:
\begin{itemize}
\item Fast: sub-millisecond latencies, with jitter around 2 ms.
\item Accurate: false negative rates under 1\% and false positive rates under 0.001\% for a variety of syllables.
\item State-of-the-art performance with default parameters.
\item Requires almost no programming experience.
\item Runs on inexpensive hardware.
\item Described in detail here, with reference implementations provided and benchmarked.
\end{itemize}

@@

Because the data set consists of temporally aligned songs, the moment
at which detection should occur during each song sample is available
(albeit with minor variations due to the alignment process used
\cite{Poole2012}).  The detector can be checked by comparing its
response to the recorded training songs against these
``canonical'' detection events.  To this end, besides the trained
network object, our learning code produces an audio file consisting of
all of the training data on the left audio channel and a delta
function at each aligned moment of target syllable presentation on the
right channel. Thus, when played on any audio player, the left channel
may be provided as input to the detector, and the the detector's
output pulses may be compared against the right channel.

@@

We define latency as the time between the training target (during our tests, this is indicated by the canonical
signal in the test file) and the corresponding detection event.  It is a helpful number,
but not a critical one; due to the stereotyped song of the zebra finch, a detector with high but
constant latency can often be trained to trigger at a point somewhat
before the true moment of interest (for example, if triggering should
occur at the very beginning of a syllable, the detector may be trained 
to recognise the previous syllable and the gap thereafter).  Usually the 
variability in latency is the more important number.  We define jitter as 
the standard deviation of detection latency, measured over the test songs.
